---
title: "serosurveillance analytic tool"
author: "Annabelle Wang"
date: "2024-02-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#install.library("stringr") 
library(readxl)
library(tidyr)
library(dplyr)
library(purrr)
library(stringr)

#######Additionall Supplementary Codes####################################################
#If need to install and poen packages from GitHub
  install.packages("devtools")
  library(devtools)
  #install_github("author/package")
  
# If need to install and open packages from Bioconductor (open source software for Bioinfomatics )
  source("http://bioconductor.org/biocLite.R")
  biocLite()
  biocLite("GenomicFeatures")
  
#To update all packages
  update.packages()
#To update one package only
  install.packages("packagename")

#To unload certain package
  detach("package:ggplot2", unload=TRUE)
#To remove certain package
  remove.packages("packagename")
  
#To check the version of R you are running
  sessionInfo()

#To get extra details on how to use a package
  browseVignettes("stringr")
  
```

#Version Control
(aka. records changes that are made to a file or a set of files over time. As you make edits, the version control system takes snapshots of your files and the changes and then saves those snapshots so you can refer, revert back to previous versions later if need be.)
 
  #GitHub Terminologies
  #[Repository]: Files are hosted in [repository] that is shared online with collaborators
  #[Pull]: You [pull] the repository's contents so that you have a local copy of the files that you can edit. 
  #[Stage] & [Commit]: Once you are happy with your changes to a file, you [stage] the file and then [commit] it.
  #[Push]: You [push] this [commit] to the shared repository. This uploads your new file and all of the changes and is accompanied by a message explaining what changed, why and by whom
  
  #Merge: when independent edits are identified by Git and are brought together into a single file with both sets of edits incorporated into a single unified file. 
The version control history tracks independent changes made to both the original file in the repository that others may be editing and tracking your changes on your branch and then merges the files together. 

  #Conflict: If both people made an edit to the same sentence that precludes one of the edit from being possible (i.e. Git is unable to merge the edits.), we have a conflict.
  Git recognizes this disparity, conflict and asks for user assistance in picking which edit to keep. 
  
  #Configuring Git:To link GitHub with R,go to git-scm.com/download to download and install Git on your computer. -->need to tell Git what your username and email are, so that it knows how to name each commit as coming from you. To do so, in the command prompt (either Git Bash for Windows or Terminal for Mac), type: git config --global user.name "Jane Doe" with your desired username in place of “Jane Doe.” --> Following this, in the command prompt, type: git config --global user.email janedoe@gmail.com
  
  #Comfirming your configuration: to check, confirm your changes by typing: git config --list
  
# linking an existing R proejct with GitHub
  #Part 1: Linking an preexisting R project with Git
  #1. Right click the folder containing your R project and choose 'New terminal at Folder'
  #2. In terminal,tap [ git init ] followed by [ git add .]
  #3. To commit these changes to Git, tap [git commit -m "Initial commit" ]
  
  #Part 2: :Linking this project with GitHUb  
  #1. go to GitHub.com and creat a new repository
  *Make sure the name is the 'exact name' as your R project
  *Do NOT initialize a README file, .gitignore, or license.
  
  #2. Upon creating the repository, you should see a section named ' ...or push an existing respository from the command line'
  #3.  In Git Bash or Terminal, copy and paste these lines of code to link your repository with GitHub.
  #4. After doing so, refresh your GitHub page
  #5. When you reoopen the R project, you should now have access to the Git tab in the upper right quadrant and can push to GitHub from within RStudio any future changes.
  
# Import and clean the original terms:

```{r}
#getwd()

######################Import specific Excel sheet:
orig_term <- read_excel("/Users/aw/Downloads/IDD/R tools/Antigen taxonomy.xlsx")
#tags<- read_excel("/Users/aw/Downloads/IDD/R tools/Antigen taxonomy.xlsx", sheet = "Covidence Tags") 
tags<- read_excel("/Users/aw/Downloads/IDD/R tools/Antigen taxonomy.xlsx", sheet = "Covidence Tags new") 


######################Clean Sheet 1: 
#names(orig_term) #get column names
clean_term <- orig_term[, c(2, 18, 19, 20, 21, 22)] #only keep 6 variables of interest: Biomarker, Common Name of Disease, Scientific  Names of pathogen, Other names, MeSh terms, Entry terms

#convert blank cell to NA
clean_term <- clean_term %>% mutate_all(na_if,"")
#clean blank rows
clean_term <- clean_term %>% 
                filter(!if_all(c(everything()), is.na)) 
clean_term <- clean_term %>%
  mutate(across(everything(), ~ifelse(str_trim(.) == "", NA, .))) #to change all columns at once; remove the white space from start and end of string, re-code columns ???
clean_term <- clean_term %>% 
  drop_na(Biomarker)  # drop rows with missing values for biomarker


######################Clean Sheet Covidence Tags new: 
#recode values
#tags_new<-tags_new%>%mutate(Tag1=recode(Tag1,"Entric"="Enteric"))
tags<-tags%>%select(1:9)

```

# Search terms for Luminex: 

```{r}
Luminex_terms <- paste('
(((“Multiplex”[tw] OR “Multiplexed”[tw] OR “Simultaneous Quantitative Detection*“[tw] OR “multiple”[tw] OR “integrated”[tw])
AND
(“Immunoassay”[Mesh:NoExp] OR “Immunoassay*“[tw] OR “Immuno-assay*“[tw] OR “Fluoroimmunoassay”[Mesh:NoExp] OR “Fluoroimmunoassay*“[tw] OR “Fluoroimmuno-assay*“[tw] OR “Immunofluorometric Assay*“[tw] OR “Immuno-fluorometric Assay*“[tw] OR ((“Bead*“[tw] OR “Microspheres”[Mesh] OR “Microsphere*“[tw] OR “Micro-Sphere*“[tw]  OR “Microbead*“[tw] OR “Latex Particle*“[tw] OR “Latex Sphere*“[tw] OR “Serological”[tw] OR “Serologic”[tw] OR “antibody”[tw] OR “antibodies”[tw]) AND “assay”[tw]))) OR
“Luminex”[tw] OR “Bead-Based Assay*“[tw] OR “Serosurveillance”[tw] OR “Serological Surveillance*“[tw] OR “Serologic Surveillance*“[tw] OR “microsphere immunoassay”[tw] OR (“validation”[tw] AND “serological”[tw]) OR “seroepidemiology”[tw] OR (“Serolog*“[tw] AND “Surveillance”[tw]) ) AND (1990:2023[pdat]) AND (excludepreprints[Filter])')


#OR "Serological"[tw] OR "Serologic"[tw] 
```

# Functions for process every cell and combine to a search term:

```{r}
# Functions for extract terms from cell contents:

# Process function for Biomarker/Common/Scientific/Other names:
process_terms <- function(cell_content) {
  # Extract terms within parentheses
  terms_in_parentheses <- gregexpr("\\(([^)]+)\\)", cell_content, perl = TRUE)
  additional_terms <- regmatches(cell_content, terms_in_parentheses)[[1]]
  additional_terms <- gsub("\\(|\\)", "", additional_terms) # Remove parentheses

  # Remove parentheses and content within from the original string
  cell_content <- gsub("\\(.*?\\)", "", cell_content)

  # Split by semicolon 
  terms <- unlist(strsplit(cell_content, ";\\s*"))
  terms <- tolower(trimws(terms))
  additional_terms <- unlist(strsplit(additional_terms, ";\\s*"))
  additional_terms <- tolower(trimws(additional_terms))

  unique(c(terms, additional_terms))
}

# Process function for Mesh terms:
process_mesh <- function(cell_content) {
  cell_content <- as.character(cell_content)
  # Split by '//' 
  terms <- unlist(strsplit(cell_content, "//\\s*"))
  terms <- trimws(terms)

  unique(terms)
}

# Process function for entry terms:
process_entry_terms <- function(cell_content) {
  cell_content <- as.character(cell_content)
  # Split by new line
  terms <- unlist(strsplit(cell_content, "\n|//\\s*"))
  terms <- tolower(trimws(terms))
  unique(terms)
}

# Function to format terms in a cell
format_terms <- function(terms) {
  #unique_terms <- unique(terms) # Remove duplicated terms in every cell
  formatted_terms <- sapply(terms, function(term) paste0('"', term, '"'))
  paste(formatted_terms, collapse = "\n")
}

# Process and format terms for each row vector
#use \n to force a new line
process_row_all_vector <- function(row_vector) {
  tibble(
    pathogen = row_vector["Biomarker"],
    #mesh_new = list(format_terms(process_mesh(unlist(strsplit(row_vector["MeSH terms"], "\n"))))),
    MeSH_new = list(format_terms(na.omit(unique(process_mesh(unlist(strsplit(row_vector["MeSH terms"], "\n"))))))),
    Entry_new = list(format_terms(na.omit(unique(c(
      #process_terms(unlist(strsplit(row_vector["Biomarker"], "\n"))),
      #process_terms(unlist(strsplit(row_vector["Common Name of Disease"], "\n"))),
      process_terms(unlist(strsplit(row_vector["Scientific Name of Pathogen"], "\n"))),
      #process_terms(unlist(strsplit(row_vector["Other names"], "\n"))),
      process_entry_terms(unlist(strsplit(row_vector["Entry terms"], "\n")))
    )))))
  )
}

# Function to create search term from a row
create_search_term <- function(mesh_terms, entry_terms) {
  # Remove NA and empty strings
  mesh_terms <- mesh_terms[!is.na(mesh_terms) & mesh_terms != ""]
  entry_terms <- entry_terms[!is.na(entry_terms) & entry_terms != ""]
  
  # Create search terms with [Mesh] and [tw] if they are not empty
  mesh_search_with_Mesh <- if (length(mesh_terms) > 0) paste(paste0(mesh_terms, "[Mesh]"), collapse = " OR ") else NULL
  mesh_search_with_tw <- if (length(mesh_terms) > 0) paste(paste0(mesh_terms, "[tw]"), collapse = " OR ") else NULL
  entry_search_with_tw <- if (length(entry_terms) > 0) paste(paste0(entry_terms, "[tw]"), collapse = " OR ") else NULL

  # Combine mesh and entry searches with OR, if they exist
  full_search <- paste(na.omit(c(mesh_search_with_Mesh, mesh_search_with_tw, entry_search_with_tw)), collapse = " OR ")
  return(full_search)
}


```

#Functions to generate disease-specific table with formatted MeSH and entry terms and search terms
```{r}
#Functions for customixed choice of tag or pathogen combinations
custSearch<-function(pathogen=NULL, Tag1=NULL, Tag1_sub=NULL,Tag2=NULL){
  
  
  
}

#Function for customized choice of tag combinations and selection of specific tag for eqch tag type
searchterms_tagComb<-function(Tag1=NULL, Tag1_sub=NULL, Tag2=NULL){
  
  # Filter the targeted tag
  
  # Start with filtering by Tag1
  tag1 <- as.vector(tag1)
  tag_data <- tags %>% filter(`Tag1` %in% tag1)
   tag_name = paste(gsub(" ", "_", tag1), collapse = "_") #perform replacement of all matches with gsub(pattern, replacement, strings_to_search, ignore.case=FLASE)
   
}

#Function for produce tag-specific tables with formated MeSH and entry terms
Table4disease<-function(x){
  #uses another dataset(i.e.x)to perform filtering
  x_terms<- clean_term %>%
  semi_join(x, by = c("Scientific Name of Pathogen" = "Pathogen"))  
  
  # Transfer the dataset to vector
list_of_x <- lapply(seq_len(nrow(x_terms)), function(i) {
  unlist(x_terms[i, ])
})
  # Process all vectors
processed_x <- map_df(list_of_x, process_row_all_vector)
combined_x <- left_join( processed_x, clean_term, by = c( "pathogen" = "Biomarker"))
combined_x_formatted <- combined_x %>%
  mutate(across(where(is.list), ~sapply(., function(x) paste(x, collapse = "\n"))))%>% 
  filter(!is.na(pathogen))
write.csv(combined_x_formatted, paste0("/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Serosurveillance analytic tool 2/","search_terms.csv")) 
}



#Function for produce tag-specific search terms
SearchT4disease<-function(x){
#Part1: function for produce tag-specific tables#############################
  #uses another dataset(i.e.x)to perform filtering
  x_terms<- clean_term %>%
  semi_join(x, by = c("Scientific Name of Pathogen" = "Pathogen"))  
  
  # Transfer the dataset to vector
list_of_x <- lapply(seq_len(nrow(x_terms)), function(i) {
  unlist(x_terms[i, ])
})
  # Process all vectors
processed_x <- map_df(list_of_x, process_row_all_vector)
combined_x <- left_join( processed_x, clean_term, by = c( "pathogen" = "Biomarker"))
combined_x_formatted <- combined_x %>%
  mutate(across(where(is.list), ~sapply(., function(x) paste(x, collapse = "\n"))))%>% 
  filter(!is.na(pathogen))

#Part2: Get the search term##################################################
  # Apply the function to mesh and entry terms of each row
x_search_terms <- lapply(1:nrow(combined_x_formatted), function(i) {
  mesh_terms <- strsplit(combined_x_formatted$MeSH_new[i], "\n")[[1]]
  entry_terms <- strsplit(combined_x_formatted$Entry_new[i], "\n")[[1]]
  create_search_term(mesh_terms, entry_terms)
})
  # Flatten, deduplicate, and concatenate all search terms
flat_search_terms <- unique(na.omit(unlist(x_search_terms)))
x_search_term <- paste(flat_search_terms, collapse = " OR ")
  # Print and save the final search term
cat(x_search_term)
writeLines(x_search_term, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Serosurveillance analytic tool 2/_Search_terms.txt")
  # Print and save the final search term (with Luminex terms)
Lmnx_x_search_term <- paste(Luminex_terms, " AND (", x_search_term, ")")
#cat(Lmnx_final_search_term)
writeLines(Lmnx_x_search_term,paste0("/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Serosurveillance analytic tool 2/", tag_name, "_search_terms.txt"))
}
```


#Produce disease-specific datasets
```{r}
#Get separate data sets for each specific value in Tag1
Tag1_gp<-unique(tags_new$Tag1) # a vector of different Tag1
Tag1Sub_gp<-unique(tags_new$`Tag1 subgroup`[!is.na(tags_new$`Tag1 subgroup`)])
Tag2_gp<-unique(tags_new$Tag2)#%>%as.list()

#function 
for (i in 1:length(Tag1_gp)){
  assign(paste0(Tag1_gp[i]),tags_new%>%filter(Tag1==Tag1_gp[i]),envir=.GlobalEnv)
}

#Get separate data sets based Tag1_subgroup
for (j in 1:length(Tag1Sub_gp)){
      assign(paste0(Tag1Sub_gp[j]),tags_new%>%filter(`Tag1 subgroup`==Tag1Sub_gp[j]),envir=.GlobalEnv)}
   

#Get separate data sets based Tag2
for (i in 1:length(Tag2_gp)){
     assign(paste0(Tag1_gp[i],"_",Tag2_gp[i]),tags_new%>%filter(Tag2==Tag2_gp[i],envir=.GlobalEnv))
    }

#Get separate data sets based Tag1 and Tag2
group_tag1_2<-function(x, Tag2_gp){
  sapply(Tag2_gp,
        for (k in 1:length(Tag2_gp)){
     assign(paste0(x[1,1],"_",Tag2_gp[k]), x%>%filter(Tag2==Tag2_gp[k]),envir=.GlobalEnv)
    })
}

group_tag1_2<-function(x){ for(k  in 1:length(Tag2_gp)){assign(paste0(x[1,1],"_",Tag2_gp[k]), x%>%filter(Tag2==Tag2_gp[k]),envir=.GlobalEnv)} }

lapply(Tag2_gp,group_tag1_2(VPD))

group_tag1_2(VPD,Tag2_gp)
group_tag1_2(Enteric,Tag2_gp)

VPD_split_tag2<-VPD%>%
  group_split(Tag2)
names(VPD_split_tag2)<-VPD_split_tag2%>% #Assign to names of listed data frames
  #extract the names by doing the following to each data frame:
  map(.)
  
```


# Generate new tables and search terms for the specific group of pathogen
```{r}
 Table4disease(EPItest)
SearchT4disease(EPItest)
```


##############################
# The first tag : VPD
```{r}
# uses another dataset(i.e.VPD) not to add rows or columns, but to perform filtering.
VPD_terms<- clean_term %>%
  semi_join(VPD, by = c("Scientific Name of Pathogen" = "Pathogen"))   

# Get a new table for the specific tag with new Mesh and entry terms

# Transfer the dataset to vector
list_of_VPD <- lapply(seq_len(nrow(VPD_terms)), function(i) {
  unlist(VPD_terms[i, ])
})

# Process all vectors
processed_VPD <- map_df(list_of_VPD, process_row_all_vector)

combined_VPD <- left_join( processed_VPD, clean_term, by = c( "pathogen" = "Biomarker"))
combined_VPD_formatted <- combined_VPD %>%
  mutate(across(where(is.list), ~sapply(., function(x) paste(x, collapse = "\n"))))%>% 
  filter(!is.na(pathogen))
write.csv(combined_VPD_formatted, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/VPD_search_terms.csv")

#combined_new <- clean_term
#combined_new <- left_join(combined_new, processed_VPD, by = c("Biomarker" = "pathogen"))
#combined_new_formatted <- combined_new %>%
 # mutate(across(where(is.list), ~sapply(., function(x) paste(x, collapse = "\n"))))%>% 
  #filter(!is.na(Biomarker))
#print(combined_new_formatted)

# Get the search term

# Apply the function to mesh and entry terms of each row
all_search_terms <- lapply(1:nrow(combined_VPD_formatted), function(i) {
  mesh_terms <- strsplit(combined_VPD_formatted$MeSH_new[i], "\n")[[1]]
  entry_terms <- strsplit(combined_VPD_formatted$Entry_new[i], "\n")[[1]]
  create_search_term(mesh_terms, entry_terms)
})
# Flatten, deduplicate, and concatenate all search terms
flat_search_terms <- unique(na.omit(unlist(all_search_terms)))
final_search_term <- paste(flat_search_terms, collapse = " OR ")

# Print and save the final search term
cat(final_search_term)
writeLines(final_search_term, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Search_terms_VPD.txt")
# Print and save the final search term (with Luminex terms)
Lmnx_final_search_term <- paste(Luminex_terms, " AND (", final_search_term, ")")
#cat(Lmnx_final_search_term)
writeLines(Lmnx_final_search_term, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Search_terms_VPD_Lmnx.txt")

```

#The second tag : Enteric
```{r}
# uses another dataset(i.e.VPD) not to add rows or columns, but to perform filtering.
Enteric_terms<- clean_term %>%
  semi_join(Enteric, by = c("Scientific Name of Pathogen" = "Pathogen"))   

# Get a new table for the specific tag with new Mesh and entry terms

# Transfer the dataset to vector
list_of_Enteric <- lapply(seq_len(nrow(Enteric_terms)), function(i) {
  unlist(Enteric_terms[i, ])
})

# Process all vectors
processed_Enteric <- map_df(list_of_Enteric, process_row_all_vector)

combined_Enteric <- left_join( processed_Enteric, clean_term, by = c( "pathogen" = "Biomarker"))
combined_Enteric_formatted <- combined_Enteric %>%
  mutate(across(where(is.list), ~sapply(., function(x) paste(x, collapse = "\n"))))%>% 
  filter(!is.na(pathogen))
write.csv(combined_Enteric_formatted, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Enteric_search_terms.csv")

# Get the search term

# Apply the function to mesh and entry terms of each row
all_search_terms <- lapply(1:nrow(combined_Enteric_formatted), function(i) {
  mesh_terms <- strsplit(combined_Enteric_formatted$MeSH_new[i], "\n")[[1]]
  entry_terms <- strsplit(combined_Enteric_formatted$Entry_new[i], "\n")[[1]]
  create_search_term(mesh_terms, entry_terms)
})
# Flatten, deduplicate, and concatenate all search terms
flat_search_terms <- unique(na.omit(unlist(all_search_terms)))
final_search_term <- paste(flat_search_terms, collapse = " OR ")
# Print and save the final search term
cat(final_search_term)
writeLines(final_search_term, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Search_terms_Enteric.txt")
# Print and save the final search term (with Luminex terms)
Lmnx_final_search_term <- paste(Luminex_terms, " AND (", final_search_term, ")")
#cat(Lmnx_final_search_term)
writeLines(Lmnx_final_search_term, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Search_terms_Enteric_Lmnx.txt")
```

#The third tag : NTD
```{r}
# uses another dataset(i.e.VPD) not to add rows or columns, but to perform filtering.
NTD_terms<- clean_term %>%
  semi_join(NTDs, by = c("Scientific Name of Pathogen" = "Pathogen"))   

# Get a new table for the specific tag with new Mesh and entry terms

# Transfer the dataset to vector
list_of_NTD <- lapply(seq_len(nrow(NTD_terms)), function(i) {
  unlist(NTD_terms[i, ])
})

# Process all vectors
processed_NTD <- map_df(list_of_NTD, process_row_all_vector)

combined_NTD <- left_join( processed_NTD, clean_term, by = c( "pathogen" = "Biomarker"))
combined_NTD_formatted <- combined_NTD %>%
  mutate(across(where(is.list), ~sapply(., function(x) paste(x, collapse = "\n"))))%>% 
  filter(!is.na(pathogen))
write.csv(combined_NTD_formatted, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/NTD_search_terms.csv")

# Get the search term

# Apply the function to mesh and entry terms of each row
all_search_terms <- lapply(1:nrow(combined_NTD_formatted), function(i) {
  mesh_terms <- strsplit(combined_NTD_formatted$MeSH_new[i], "\n")[[1]]
  entry_terms <- strsplit(combined_NTD_formatted$Entry_new[i], "\n")[[1]]
  create_search_term(mesh_terms, entry_terms)
})
# Flatten, deduplicate, and concatenate all search terms
flat_search_terms <- unique(na.omit(unlist(all_search_terms)))
final_search_term <- paste(flat_search_terms, collapse = " OR ")
# Print and save the final search term
cat(final_search_term)
writeLines(final_search_term, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Search_terms_NTD.txt")
```

#The forth tag : Vector
```{r}
# uses another dataset(i.e.VPD) not to add rows or columns, but to perform filtering.
Vector_terms<- clean_term %>%
  semi_join(Vector, by = c("Scientific Name of Pathogen" = "Pathogen"))   

# Get a new table for the specific tag with new Mesh and entry terms

# Transfer the dataset to vector
list_of_Vector <- lapply(seq_len(nrow(Vector_terms)), function(i) {
  unlist(Vector_terms[i, ])
})

# Process all vectors
processed_Vector <- map_df(list_of_Vector, process_row_all_vector)

combined_Vector <- left_join( processed_Vector, clean_term, by = c( "pathogen" = "Biomarker"))
combined_Vector_formatted <- combined_Vector %>%
  mutate(across(where(is.list), ~sapply(., function(x) paste(x, collapse = "\n"))))%>% 
  filter(!is.na(pathogen))
write.csv(combined_Vector_formatted, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Vector_search_terms.csv")

# Get the search term

# Apply the function to mesh and entry terms of each row
all_search_terms <- lapply(1:nrow(combined_Vector_formatted), function(i) {
  mesh_terms <- strsplit(combined_Vector_formatted$MeSH_new[i], "\n")[[1]]
  entry_terms <- strsplit(combined_Vector_formatted$Entry_new[i], "\n")[[1]]
  create_search_term(mesh_terms, entry_terms)
})
# Flatten, deduplicate, and concatenate all search terms
flat_search_terms <- unique(na.omit(unlist(all_search_terms)))
final_search_term <- paste(flat_search_terms, collapse = " OR ")
# Print and save the final search term
cat(final_search_term)
writeLines(final_search_term, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Search_terms_Vector.txt")
```

#The fifth tag : Sti
```{r}
# uses another dataset(i.e.VPD) not to add rows or columns, but to perform filtering.
Sti_terms<- clean_term %>%
  semi_join(Sti, by = c("Scientific Name of Pathogen" = "Pathogen"))   

# Get a new table for the specific tag with new Mesh and entry terms

# Transfer the dataset to vector
list_of_Sti <- lapply(seq_len(nrow(Sti_terms)), function(i) {
  unlist(Sti_terms[i, ])
})

# Process all vectors
processed_Sti <- map_df(list_of_Sti, process_row_all_vector)

combined_Sti <- left_join( processed_Sti, clean_term, by = c( "pathogen" = "Biomarker"))
combined_Sti_formatted <- combined_Sti %>%
  mutate(across(where(is.list), ~sapply(., function(x) paste(x, collapse = "\n"))))%>% 
  filter(!is.na(pathogen))
write.csv(combined_Sti_formatted, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Sti_search_terms.csv")

# Get the search term

# Apply the function to mesh and entry terms of each row
all_search_terms <- lapply(1:nrow(combined_Sti_formatted), function(i) {
  mesh_terms <- strsplit(combined_Sti_formatted$MeSH_new[i], "\n")[[1]]
  entry_terms <- strsplit(combined_Sti_formatted$Entry_new[i], "\n")[[1]]
  create_search_term(mesh_terms, entry_terms)
})
# Flatten, deduplicate, and concatenate all search terms
flat_search_terms <- unique(na.omit(unlist(all_search_terms)))
final_search_term <- paste(flat_search_terms, collapse = " OR ")
# Print and save the final search term
cat(final_search_term)
writeLines(final_search_term, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Search_terms_Sti.txt")
```

#The sixth tag : Respiratory
```{r}
# uses another dataset(i.e.VPD) not to add rows or columns, but to perform filtering.
Respiratory_terms<- clean_term %>%
  semi_join(Respiratory, by = c("Scientific Name of Pathogen" = "Pathogen"))   

# Get a new table for the specific tag with new Mesh and entry terms

# Transfer the dataset to vector
list_of_Respiratory <- lapply(seq_len(nrow(Respiratory_terms)), function(i) {
  unlist(Respiratory_terms[i, ])
})

# Process all vectors
processed_Respiratory <- map_df(list_of_Respiratory, process_row_all_vector)

combined_Respiratory <- left_join( processed_Respiratory, clean_term, by = c( "pathogen" = "Biomarker"))
combined_Respiratory_formatted <- combined_Respiratory %>%
  mutate(across(where(is.list), ~sapply(., function(x) paste(x, collapse = "\n"))))%>% 
  filter(!is.na(pathogen))
write.csv(combined_Respiratory_formatted, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Respiratory_search_terms.csv")

# Get the search term

# Apply the function to mesh and entry terms of each row
all_search_terms <- lapply(1:nrow(combined_Respiratory_formatted), function(i) {
  mesh_terms <- strsplit(combined_Respiratory_formatted$MeSH_new[i], "\n")[[1]]
  entry_terms <- strsplit(combined_Respiratory_formatted$Entry_new[i], "\n")[[1]]
  create_search_term(mesh_terms, entry_terms)
})
# Flatten, deduplicate, and concatenate all search terms
flat_search_terms <- unique(na.omit(unlist(all_search_terms)))
final_search_term <- paste(flat_search_terms, collapse = " OR ")
# Print and save the final search term
cat(final_search_term)
writeLines(final_search_term, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Search_terms_Respiratory.txt")
```


#The seventh tag : Emerging
```{r}
# uses another dataset(i.e.VPD) not to add rows or columns, but to perform filtering.
Emerging_terms<- clean_term %>%
  semi_join(Emerging, by = c("Scientific Name of Pathogen" = "Pathogen"))   

# Get a new table for the specific tag with new Mesh and entry terms

# Transfer the dataset to vector
list_of_Emerging <- lapply(seq_len(nrow(Emerging_terms)), function(i) {
  unlist(Emerging_terms[i, ])
})

# Process all vectors
processed_Emerging <- map_df(list_of_Emerging, process_row_all_vector)

combined_Emerging <- left_join( processed_Emerging, clean_term, by = c( "pathogen" = "Biomarker"))
combined_Emerging_formatted <- combined_Emerging %>%
  mutate(across(where(is.list), ~sapply(., function(x) paste(x, collapse = "\n"))))%>% 
  filter(!is.na(pathogen))
write.csv(combined_Emerging_formatted, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Emerging_search_terms.csv")

# Get the search term

# Apply the function to mesh and entry terms of each row
all_search_terms <- lapply(1:nrow(combined_Emerging_formatted), function(i) {
  mesh_terms <- strsplit(combined_Emerging_formatted$MeSH_new[i], "\n")[[1]]
  entry_terms <- strsplit(combined_Emerging_formatted$Entry_new[i], "\n")[[1]]
  create_search_term(mesh_terms, entry_terms)
})
# Flatten, deduplicate, and concatenate all search terms
flat_search_terms <- unique(na.omit(unlist(all_search_terms)))
final_search_term <- paste(flat_search_terms, collapse = " OR ")
# Print and save the final search term
cat(final_search_term)
writeLines(final_search_term, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Search_terms_Emerging.txt")
```


#The fifth tag : Other
```{r}
# uses another dataset(i.e.VPD) not to add rows or columns, but to perform filtering.
Other_terms<- clean_term %>%
  semi_join(Other, by = c("Scientific Name of Pathogen" = "Pathogen"))   

# Get a new table for the specific tag with new Mesh and entry terms

# Transfer the dataset to vector
list_of_Other <- lapply(seq_len(nrow(Other_terms)), function(i) {
  unlist(Other_terms[i, ])
})

# Process all vectors
processed_Other <- map_df(list_of_Other, process_row_all_vector)

combined_Other <- left_join( processed_Other, clean_term, by = c( "pathogen" = "Biomarker"))
combined_Other_formatted <- combined_Other %>%
  mutate(across(where(is.list), ~sapply(., function(x) paste(x, collapse = "\n"))))%>% 
  filter(!is.na(pathogen))
write.csv(combined_Other_formatted, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Other_search_terms.csv")

# Get the search term

# Apply the function to mesh and entry terms of each row
all_search_terms <- lapply(1:nrow(combined_Other_formatted), function(i) {
  mesh_terms <- strsplit(combined_Other_formatted$MeSH_new[i], "\n")[[1]]
  entry_terms <- strsplit(combined_Other_formatted$Entry_new[i], "\n")[[1]]
  create_search_term(mesh_terms, entry_terms)
})
# Flatten, deduplicate, and concatenate all search terms
flat_search_terms <- unique(na.omit(unlist(all_search_terms)))
final_search_term <- paste(flat_search_terms, collapse = " OR ")
# Print and save the final search term
cat(final_search_term)
writeLines(final_search_term, "/Users/aw/Downloads/IDD/R tools/serosurveillance analytic tool/Search_terms_Other.txt")
```

# Trash cood
```{r}
##############################################
# re-code value
#VPD<-tags_filled%>%
#  filltr(Tag=="VPD")
#VPD<-VPD%>% mutate(Tag_subgroup=recode(Tag_subgroup,
#                                       #for reference old = new
#                                      "13 childhood EPI VPDs (WHO Recommendations)"="EPI VPDs") )
# Population tag_subgroup with the corresponding group
#VPD<-VPD%>%
#  mutate(Tag_subgroup=ifelse(str_trim(Tag_subgroup)=="",NA,Tag_subgroup))%>%
#  fill(Tag_subgroup, .direction = "down")

##############################################

######################Clean Sheet Covidence Tags: 
#rename colume names
colnames(tags)[6]="Tag_subgroup"
#remove blank columns
tags<-tags %>% 
  select(-c(5,7))
#recode values
tags<-tags%>% mutate(Tag_subgroup=recode(Tag_subgroup,"13 childhood EPI VPDs (WHO Recommendations)"="EPI VPDs") )

#convert blank cell to NA
tags <- tags %>% mutate_all(na_if,"")
#clean blank rows
tags <- tags %>% 
                filter(!if_all(c(everything()), is.na)) 
tags <- tags %>%
  mutate(across(everything(), ~ifelse(str_trim(.) == "", NA, .)))
# drop rows with missing values for Pathogen
#tags <- tags %>% 
#  drop_na(Pathogen)  # drop rows with missing values for biomarker

tags_filled <- tags %>%
  mutate(Tag = ifelse(str_trim(Tag) == "", NA, Tag))%>%
  fill(Tag, .direction = "down") # Populate tags with the corresponding group
```